---
title: "Final Projectplot"
author: "Mohamed Tausif Siddiqui ,Zoel Quinonez,Neyousha Shahisavandi"
date: "2020-10-24"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

The purpose of this code is to take both the wage and unemployment datasets from 
the CA DPH and clean the data so that it can be used for analysis.  As part of 
this, we eliminate columns unnecessary for analysis.  We also eliminate rows 
where relevant wage, unemployment, race/ethnicity and region specific data is missing, as these will be the basis for the analysis.  We create at least two 
new variables for each of the data sets.  We provide some descriptive statistics 
and perform and initial examination of the means by plotting unemployment and 
wage data by race/ethnicity and region.

###  Loading Libraries and Data Files
Data Source:https://data.chhs.ca.gov/dataset


```{r,include=F,echo=F}

library(tidyverse)
library(readxl)
library(stringr)
library(plotly)
library(kableExtra)
library(ggplot2)
library(gplots)
library(formattable)
library(DT)
```

## Importing and examining the data
```{r,include=F,echo=F}
# Downloading Data Files 

url_wage <- "https://data.chhs.ca.gov/dataset/442e7cde-6230-405c-b8a8-b7ea5489de87/resource/f5a57e7a-e0fe-4d80-b0f6-92d66ecb907f/download/hci_living_wage_770_pl_co_re_ca_9-29-13-ada.xlsx"
wage_file <- "hci_living_wage.xlsx"
curl::curl_download(url_wage, wage_file)

url_unemp <- "https://data.chhs.ca.gov/dataset/1be8df02-922b-4d34-9afc-c8b3c6f9be54/resource/2ecd7fda-2317-4fa1-8a6e-1834cfa39cc0/download/hci_unemployment_290_ca_re_co_cd_pl_ct-5-22-14-ada.xlsx"
unemp_file <- "hci_unemployment.xlsx"
curl::curl_download(url_unemp, unemp_file)



# Downloading Data Dictionaries
url_wagedd <- "https://data.chhs.ca.gov/dataset/442e7cde-6230-405c-b8a8-b7ea5489de87/resource/f6ae935b-d0ba-4be2-be35-717fe42ecc6c/download/livingwage-dd.xlsx"
wage_dd_file <- "livingwage-dd.xlsx"
curl::curl_download(url_wagedd, wage_dd_file)

url_unempdd <- "https://data.chhs.ca.gov/dataset/1be8df02-922b-4d34-9afc-c8b3c6f9be54/resource/6c6311f0-827e-4b9e-836a-8e5cd33e2e40/download/unemploymentdd.xlsx"
unemp_dd_file <- "unemploymentdd.xlsx"
curl::curl_download(url_unempdd, unemp_dd_file)



# Loading Data Files
hci_unemployment_290 <- read_excel(unemp_file,n_max=106410)
# last row 106411 is empty
hci_living_wage <- read_excel(wage_file,n_max=15869)
#last row 15870 is empty



# Loading Data Dictionaries Files
data_dictionary_hci_living_wage <- tibble(read_excel(wage_dd_file))
hci_unemployment_dictiionary <- tibble(read_excel(unemp_dd_file))
```
```{r,echo=T}

str(hci_living_wage)
head(hci_living_wage, 100)

# Ensuring that name data and code data have same number of categories
unique(hci_living_wage$race_eth_name)
unique(hci_living_wage$race_eth_code)
unique(hci_living_wage$region_name)
unique(hci_living_wage$region_code)

# figuring out categories for family
unique(hci_living_wage$family_type)

# Ensuring that name data and code data have same number of categories
unique(hci_unemployment_290$race_eth_name)
unique(hci_unemployment_290$race_eth_code)
unique(hci_unemployment_290$region_name)
unique(hci_unemployment_290$region_code)

# figuring out categories for family
unique(hci_unemployment_290$family_type)

# figuring out how many different year categories and how many rows for 2010
unique(hci_unemployment_290$reportyear)


```

```{r,echo=F}


hci_unemployment<-hci_unemployment_290[-c(106410),]

```
```{r,echo=F}



hci_living_wage_h<-hci_living_wage[,-c(17:20)]
hci_living_wage_h<-hci_living_wage_h[-c(15869),]
```


First we want to see which counties have a living wage of over $30.00 for the family groups. 

```{r,echo=F}
over_30dollars_living_wage<-ifelse(hci_living_wage_h$livingwage>30,"Yes","No")
hci_living_wage_h<-cbind(hci_living_wage_h,over_30dollars_living_wage)
```
Next, we want to see if the data belongs to Native families who have children,so we create a new column.Since our data is not cleaned yet, we need to consider both "child" and "Child". 
```{r,echo=F}

Native_Family_with_minor<-tibble(if_else(str_detect(hci_living_wage_h$family_type,"hild")&(hci_living_wage_h$race_eth_name=="AIAN"),"Native with minor","No",missing=NULL))
hci_living_wage_h<-add_column(hci_living_wage_h,Native_Family_with_minor,.after = 5)
colnames(hci_living_wage_h)[6]<-"nativefam_with_minor"

```
Now, we move to the unemployment data. We want to create a column where it shows the difference of percentage of unemployment on each row versus the national unemployment average, which is 7.9%
```{r,echo=F}

Unemployed_rate_difference<-(hci_unemployment$Unemployment_rate-7.9)
unemployment<-add_column(hci_unemployment,Unemployed_rate_difference,.after=15)
colnames(unemployment)[16]<-"unemployment_VS_national"

```
\newpage 
### Cleaning DATA and Recoding
first , we drop columns with all NA values. There are four in the Unemployment table.There are columns with constant values, we drop those too.
```{r, echo=F}

unemployment<-select(unemployment,-c(ind_id,ind_definition,ll_95ci,ul_95ci,se,place_decile,rse,ind_id,ind_definition,version))
unemployment<-as.data.frame(na.omit(unemployment))
hci_living_wage_h<-select(hci_living_wage_h,-c(ind_definition,ind_id,reportyear,race_eth_code,geotypevalue,geotype,region_code,family_type_decile))

#we drop the NA rows on the Living wage table too
hci_living_wage_1<-na.omit(hci_living_wage_h)

```
##It is important to note lots of the variables are dropped, and the the total race is shown only. We could keep the previous data and work with hci_living_wage_h . Also, we change the region code in Unemployment data to numeric
```{r, echo=F}

unemployment$region_code<-as.numeric(unemployment$region_code)
```

\newpage

###DATA DICTIONARY
##Living Wage:
```{r , echo=T}
library(kableExtra)
kable(data_dictionary_hci_living_wage)
```
\newpage
###DATA DICTIONARY
##Unemployment
```{r, echo=T}

kable(hci_unemployment_dictiionary)
```
\newpage
###Descriptive Statistics for Living Wage Data
```{r, echo=T}
Living_wage_average<- c(summary(hci_living_wage_1$livingwage))
Families_under_living_wage<-c(summary(hci_living_wage_1$fam_lt_lw))
Families_percent_under_living_wage<-c(summary(hci_living_wage_1$pct_lt_lw))
average_number_of_families<-c(summary(hci_living_wage_1$families))
Descriptive<-tibble(Living_wage_average,Families_percent_under_living_wage,Families_under_living_wage,average_number_of_families)
data_<-c("Min","1st Qu.","Median","Mean","3rd Qu.","Max." )
Descriptive<-cbind(data_,Descriptive)
print(Descriptive)
```
\newpage
###Descriptive Statistics for Unemployment Data
```{r, echo=T}
Unemployment_count<-c(summary(unemployment$Unemployment))
Labour_force_count<-c(summary(unemployment$Labor_force))
Unemployment_percent_average<-c(summary(unemployment$Unemployment_rate))
Unemployment_rate_difference_average<-c(summary(unemployment$unemployment_VS_national))
Descriptive2<-tibble(Unemployment_count,Labour_force_count,Unemployment_percent_average,Unemployment_rate_difference_average)
data_<-c("Min","1st Qu.","Median","Mean","3rd Qu.","Max." )
Descriptive2<-cbind(data_,Descriptive2)
print(Descriptive2)
```
\newpage
### Bar Chart :Los Angeles Top 6 Regions With The Highest Unemployment Rates 2006-2010
Interpretation:
This is a bargraph showing the top 6 regions in Los Angeles with the highest rates of total unemployment. Desert View Highlands has the highest unemployment rate, 21.2%. Based on 2010 census, this area has about 2,360 population with about 50% whites and 50% Africans and Latinos. 

```{r, results='hide'}
unemployment_total<-filter(unemployment,race_eth_name=="Total",reportyear=="2006-2010",county_name=="Los Angeles",Unemployment_rate>14.99)
ggplot(unemployment_total, aes(x = geoname, y = Unemployment_rate)) +
  geom_col(fill =rainbow(n=length(unemployment_total$geoname)), color = "blue",width = 0.85,position = 'dodge') +
  labs(x = "Regions",
       y = "Unemplyment Rate (%)",
       title = "Los Angeles Top 6 Regions With The Highest Unemployment Rates 2006-2010")+theme(axis.text.x = element_text(size = 7))+geom_text(aes(label=Unemployment_rate), position=position_dodge(width=0.9), vjust=-0.25)
  theme_bw()


```
```{r,echo=F}
#Freeing memory by deleting large intermediate objects
rm(hci_living_wage_h)
rm(hci_living_wage_1)
rm(hci_unemployment)
rm(data_dictionary_hci_living_wage)
rm(hci_unemployment_dictiionary)
rm(unemployment)
rm(Native_Family_with_minor)
rm(unemployment_total)
```

\newpage
### Cleaning Data  to compare Unemployment Rate verses Time for different 
### Regions of California
##  Generate Table to show UnEmployment Rates Across various MPO based 
##  California Regions from 2004-2013
```{r,echo=F}

ds<-hci_unemployment_290 %>%
#select only specific colums 
  select(c(reportyear,race_eth_name,region_name,Unemployment_rate))%>%
  
  #remove rows with  which are na 
  #beacause the race is specific for adding California regions
  drop_na(region_name)%>%  
  
  #remove rows with race specific distiction and keep only total
  filter(race_eth_name=="Total")%>%
  
  #remove rows with period interval instead of specific year
  filter(!grepl("-",reportyear ))%>%
  
  #remove rows with missing values of unemployment data 
  drop_na(Unemployment_rate)%>%
  
  # removes columns that were kept for cleaning purposes
  select(reportyear,region_name,Unemployment_rate)%>%
  
  #group data based on year and region
  group_by(reportyear,region_name)%>%
  summarize(Rate=mean(Unemployment_rate))

 
```
```{r, echo=T}
kable(ds,booktabs=T,align='lcr',
      digits=c(0,0,1),
      caption="UnEmployment Rates Across various MPO Based CA Regions from 2004-2013",
      col.names=c("Year","MPO CA Region","UnEmployment Rate"))    %>%
     kable_styling(full_width=T) %>%
 footnote(
    general="Case data is from the CDPH accessed via the CHHS Open Data portal.. ",
    general_title="Data Sources",
    title_format=c("italic"),
    threeparttable=T
  )
```

\newpage
### Scatter line plot for Time based 
### Unemployment Rates across all MPO based CA  Regions.
   

###Interpretation: 
##A general trend is observed as there is a rise in unemployment rate from to 
##2006 to 2010 and with the peak in 2010 for all regions and 
##then again the unemployment rate started declining from 2010 to 2013
  

```{r warning=FALSE, echo=T}

unemployment_vs_time_plot<-ds%>%ungroup()%>%plot_ly(
  x=~reportyear,
  y=~Rate,
  color=~region_name,
  type="scatter",
  mode="lines",
  colors = c("pink","green","red","orange","blue", "skyblue","darkgreen", "darkorange","darkred","purple","skyblue","magenta","beige","maroon"),
  text = ~paste('Year: ',reportyear,'<br>Region: ',region_name,'<br>Rate: ',Rate)
) %>%
  layout(
    title="UnEmployment Rates across Various California MPO regions, 2004-2013",
    yaxis=list(title="Unemploment Rate "),
    xaxis=list(title="Year")
    
  )
unemployment_vs_time_plot
```

```{r,echo=F}
#Freeing memory by deleting large intermediate objects
rm(ds)
rm(unemployment_vs_time_plot)

```

\newpage

## Wage data manipulation
```{r wage-data-prep,echo=F}

# ***STRATEGY FOR DATA PREPARATION -- WAGE DATA***

# will assess region as confounder for race/ethnicity so 
# will eliminate county_name, county_fips given overlapping data with region
# will eliminate geotype and geotypevalue columns
# will eliminated 95CI categories, SE and RSE given that they are missing and not
# needed for analysis

# will eliminate version column
# will eliminate ind_id and ind_definition columns, as they are all the same

wage_data_2 <- select(hci_living_wage, -c("county_name","county_fips","geotype","geoname",
                                  "geotypevalue", "LL_95CI", "UL_95CI", "se", 
                                  "rse", "version", "ind_id", "ind_definition",
                                  "family_type_decile"))

view(wage_data_2)

# will eliminate all rows for which there is race/ethnicity or region missing
# will eliminate rows for which % below living wage data is missing
# will eliminate any rows with family data is missing
# will eliminate "Adult1_children" or "Adult2_children" even though
# this may be biased by region of ethnicity/race

wage_data_fix <- wage_data_2 %>%
  drop_na(race_eth_code) %>%
  drop_na(race_eth_name) %>%
  drop_na(region_code) %>%
  drop_na(pct_lt_lw) %>%
  drop_na(region_name) %>%
  mutate(num_fam = case_when(family_type == "Adult1" ~ as.character(1), 
                             family_type %in% c("Adult1_Child1", "Adults2") ~ as.character(2),
                             family_type %in% c("SingleMother2Children", "Adult2_Child1", "Adult1_Children2") ~ as.character(3), 
                             family_type %in% c("MarriedCouple2Children","Adult1_Children3", "Adults2_Children2") ~ as.character(4),
                             family_type == 
                               "Adult2_Children3" ~ as.character(5),
                             TRUE ~ NA_character_)
         )

# change all column names to lower case
wage_data_fix <- set_names(wage_data_fix, tolower(names(wage_data_fix[1:12])))
view(wage_data_fix)

# New variables left to create:
#   how many people in the household
#   categories for % below living wage based on highest and lowest % in data set
#   transform pct_lt_lw given that zeros make it difficult to calculate a RR

```

\newpage

## Unemployment data manipulation
```{r unemp-data-prep,echo=F}

# ***STRATEGY FOR DATA PREPARATION -- UNEMPLOYMENT DATA***

# will assess region as confounder for race/ethnicity so will 
# eliminate geotype categories
# eliminate county_name, county_fips given overlapping data with region
# will eliminated 95CI categories, SE and RSE as they are not needed for analysis
# will eliminate version category

unemp_data_2 <- select(hci_unemployment_290, -c("county_name","county_fips","geotype","geoname",
                                  "geotypevalue", "ll_95ci", "ul_95ci", "se", 
                                  "rse", "version", "ind_id", 
                                  "ind_definition"))

# will eliminate all rows for which there is race/ethnicity or region missing
# will eliminate any rows with missing values for Unemploymeny_rate, or where it cannot be
# calculated from Unemployment and Labor_force

unemp_data_fix <- unemp_data_2 %>%
  drop_na(race_eth_code) %>%
  drop_na(race_eth_name) %>%
  drop_na(region_code) %>%
  drop_na(region_name) %>%
  drop_na(Unemployment_rate)

# will eliminate any rows with missing values for Unemploymeny_rate, or where
# it cannot be calculated from Unemployment and Labor_force# subsetting to years 
# 2006-2010 and 2010 only "total" available for race_eth_name for year 2010 
# so elected to include 2006-2010

unemp_data_fix <- subset(unemp_data_fix, reportyear %in% c("2010", "2006-2010"))

# change all column names to lower case
unemp_data_fix <- set_names(unemp_data_fix, 
                            tolower(names(unemp_data_fix[1:10])))
view(unemp_data_fix)

```

\newpage

## Creating new variables for both the living wage and unemployment data
```{r var-create,echo=F}

# ***VARIABLES FOR WAGE DATA***

# identifying min and max for perentage of families below a living wage
max(wage_data_fix$pct_lt_lw)
min(wage_data_fix$pct_lt_lw)

# given values of zero, will log transform all the data after adding 
# a constant (2)
log_pct <- c(log10(wage_data_fix$pct_lt_lw + 2))
wage_data_trans <- cbind(wage_data_fix, log_pct)

# creating 4 categories for percentage of families below a living wage
wage_data_trans <- wage_data_trans %>%
  mutate(quart_lvg_wage = 
           case_when(pct_lt_lw < 25 ~ as.character(1),
                     pct_lt_lw >= 25 & pct_lt_lw < 50 ~ as.character(2),
                     pct_lt_lw >= 50 & pct_lt_lw < 75 ~ as.character(3),
                     pct_lt_lw >= 75 ~ as.character(4),
                     TRUE ~ NA_character_)
  )

# summarizing data to percentage of families 
# below living wage by race and region
wage_data_final <- wage_data_trans %>%
  group_by(region_name, race_eth_name) %>%
  summarise(mean_below_wg = mean(pct_lt_lw)) %>%
  pivot_wider(names_from = region_name,
              values_from = mean_below_wg)

# ***VARIABLES FOR UNEMPLOYMENT DATA***

# variables for min and max unemployment rate and one-fourth the difference
(maxR <- max(unemp_data_fix$unemployment_rate))
(minR <- min(unemp_data_fix$unemployment_rate))
(fourth_diff <- (maxR - minR)/4)

# creating three cut-offs for unemployment rate
(a <- minR + fourth_diff)
(b <- minR + 2*fourth_diff)
(c <- maxR - fourth_diff)

# quartiles for unemployment rate based on highest and lowest rate in data set
unemp_data_fix <- unemp_data_fix %>%
  mutate(quart_unemp = 
           case_when(unemployment_rate < a ~ as.character(1),
                     unemployment_rate >= a & unemployment_rate < b ~ as.character(2),
                     unemployment_rate >= b & unemployment_rate < c ~ as.character(3),
                     unemployment_rate >= c ~ as.character(4),
                     TRUE ~ NA_character_)
         )

# summarizing data to percentage of families 
# below living wage by race and region
unemp_data_final <- unemp_data_fix %>%
  group_by(region_name, race_eth_name) %>%
  summarise(mean_unemp = mean(unemployment_rate)) %>%
  pivot_wider(names_from = region_name,
              values_from = mean_unemp)

# # joining unemployment and wage data by region and race
# final_unemp_wge <- 
#   inner_join(wage_data_final, unemp_data_final, 
#              by = c("region_name", "race_eth_name")) 

```

\newpage

## Descriptive statistics and plots for both datasets
# Table for wage data
```{r table-plots,echo=T}
formattable(
wage_data_final,
digits = 2,
row.names = FALSE,
col.names = c("Race/Ethnicity", names(wage_data_final)[-1]),
caption = "Percent Below Living Wage by Race and Region"
)
```
\newpage
# Table for unemployment data
```{r table,echo=T}

formattable(
unemp_data_final,
digits = 2,
row.names = FALSE,
col.names = c("Race/Ethnicity", names(unemp_data_final)[-1]),
caption = "Unemployment Rate by Race and Region"
)
```
# subsetting data for wage and unemployment
```{r, echo=F}
wage_plot_data <- wage_data_fix %>%
  group_by(race_eth_name, region_name) %>%
  summarise(mean_below_wg = mean(pct_lt_lw)) %>%
  select(race_eth_name, region_name, mean_below_wg)

unemp_plot_data <- unemp_data_fix %>%
  group_by(race_eth_name, region_name) %>%
  summarise(mean_unemp = mean(unemployment_rate)) %>%
  select(race_eth_name, region_name, mean_unemp)
```
\newpage
## bar graphs for wage per race data by region
## Interpretation: 
## The percentage of household for different racial/ethnic groups 
## living below a living wage varies across regions.  The overall trend 
## demonstrates that across regions, Latino, African American and American 
## Indian / Alaska Native populations have a larger proportions of their 
## families living below a living wage.

```{r, echo=T}

ggplot(data = wage_plot_data, aes(x = race_eth_name, y = mean_below_wg)) +
  geom_bar(stat = "identity", aes(fill = race_eth_name),
            show.legend = TRUE) +
  scale_fill_discrete(name = "Race/Ethnicity") +
  labs(title = "Household Income Below Living Wage by Race and Across Regions",
       subtitle = "For 2010", y = "Percent Below Living Wage", x = "") +
  facet_grid(rows = vars(race_eth_name)) +
  facet_wrap(~ region_name, ncol = 4) +
  theme_minimal() +
  theme(strip.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(limits = c(0,100))
```
\newpage
## bar graphs for Unemployment rate per race data by region

## Interpretation: 
## The unemployment rate for different racial/ethnic groups varies 
## across regions.  The overall trend demonstrates that across regions, 
## African American and American Indian / Alaska Native populations tend to
## have a higher unemployment rate, while White and Asian populations tend to
## have a lower unemployment rate.

```{r, echo=T}
ggplot(data = unemp_plot_data, aes(x = race_eth_name, y = mean_unemp)) +
  geom_bar(stat = "identity", aes(fill = race_eth_name),
            show.legend = TRUE) +
  scale_fill_discrete(name = "Race/Ethnicity") +
  labs(title = "Unemployment Rate by Race and Across Regions",
       subtitle = "For 2010", y = "Percent Unemployment", x = "") +
  facet_grid(rows = vars(race_eth_name)) +
  facet_wrap(~ region_name, ncol = 4) +
  theme_minimal() +
  theme(strip.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(limits = c(0,75))
```
\newpage
## plotting overall CA percentage of those below a living wage by ethnicity/race
## Interpretation:
## When looking at the entirety of California, Latinos have a higher proportion
## of households living below a living wage when compared to the total
## population as well as when compared to Whites.  This is statistically
## significant.

```{r, echo=T,warning=F}

plotmeans(pct_lt_lw ~ race_eth_name, data = wage_data_trans, ci.label = TRUE,
          mean.label = FALSE, digits = 1, ylim = c(30, 70),
          cex.main = 1, cex.axis = 0.6, n.label = FALSE,
          barcol = "blue", col = "black",
          connect = FALSE,
          ylab = "Percent below living wage (mean +/- CI)",
          xlab = "Race / Ethnicity",
          main = "Percentage of those living below a living wage by race
          / ethnicity in CA")

```
\newpage

# plotting overall CA unemployment rate by ethnicity / race
## Interpretation:
## When looking at the entirety of California, American Indian / Alaska Natives
## have a higher proportion of unemployed when compared to all except African
## Americans.  African Americans have a higher proportion of unemployed than
## all but American Indian / Alaska Natives, as well as Hawaiian / Pacific
## Islander.  Asians have a higher proportion of employed when compared to all
## other race / ethnic groups.  Whites have a higher proportion of employed when
## compared to all groups other than Asians. This is statistically significant.

```{r, echo=T,,warning=F}

plotmeans(unemployment_rate ~ race_eth_name, data = 
            unemp_data_fix, ci.label = TRUE, 
          mean.label = FALSE, digits = 1, ylim = c(5, 18),
          cex.main = 1, cex.axis = 0.6, n.label = FALSE,
          barcol = "blue", col = "black",
          connect = FALSE,
          ylab = "Unemployment Rate (mean +/- CI)",
          xlab = "Race / Ethnicity",
          main = "Total CA unemployment rate by race / ethnicity")

```
\newpage

## Creating the data dictionary

```{r data_library, echo=F}

data_dict <- tibble(
    'Variable Name' = c("reportyear", "family_type", "race_eth_code",
                        "race_eth_name", "region_name", "region_code",
                        "fam_lt_lw", "families",
                        "pct_lt_lw", "ca_rr", "livingwage", "num_fam",
                        "log_pct", "quart_lvg_wage", "unemployment",
                        "labor_force", "unemployment_rate", "place_decile", 
                        "mean_below_wg", "mean_unemp"),
    'Description' = c("year for which the data is aggregated", 
                      "member makeup of family", 
                      "code assigned to race/ethnicity designation", 
                      "race/ethnicity designation", 
                      "MPO specific region",
                      "MPO-based region code", 
                      "number of families below a living wage", 
                      "total number of families", 
                      "percentage of size-specific families making below
                      a living wage", 
                      "rate ratio to CA rate",
                      "living wage rate for region", 
                      "total persons per family", 
                      "log transformation of pct_lt_lw plus two", 
                      "categories of percent people living below living wage",
                      "unemployed population", 
                      "population in the labor force",
                      "(unemployment/labor_force)*100", 
                      "CA deciles for unemployment", 
                      "percent of all families making below a living 
                      wage throughout the region", 
                      "percent unemployment in this region"),
    'Type' = c(typeof(wage_data_trans$reportyear),
               typeof(wage_data_trans$family_type), 
               typeof(wage_data_trans$race_eth_code), 
               typeof(wage_data_trans$race_eth_name), 
               typeof(wage_data_trans$region_name), 
               typeof(wage_data_trans$region_code), 
               typeof(wage_data_trans$fam_lt_lw), 
               typeof(wage_data_trans$families), 
               typeof(wage_data_trans$pct_lt_lw), 
               typeof(wage_data_trans$ca_rr), 
               typeof(wage_data_trans$livingwage), 
               typeof(wage_data_trans$num_fam), 
               typeof(wage_data_trans$log_pct), 
               typeof(wage_data_trans$quart_lvg_wage), 
               typeof(unemp_data_fix$unemployment), 
               typeof(unemp_data_fix$labor_force), 
               typeof(unemp_data_fix$unemployment_rate), 
               typeof(unemp_data_fix$place_decile), 
               typeof(wage_plot_data$mean_below_wg), 
               typeof(unemp_plot_data$mean_unemp))
    
)
```
```{r , echo=T}
kable(data_dict,booktabs=T,align='lcr')    %>%
     kable_styling(full_width=T)
```
```{r , echo=F}
rm(unemp_data_2)
rm(unemp_data_fix)
rm(wage_data_2)
rm(wage_data_fix)
rm(wage_data_trans)

```